Import processed data
```{r}
data = read.csv("../data/processed/multi_var_unscaled.csv", header = TRUE)
data = na.omit(data)
head(data)
```

```{r}
colnames(data)
```
```{r}
hosp_cor = cor(data, data$HospCt)
hosp_cor
#str(hosp_cor)



cor(data)
```



library(ppcor)
cor.test(x = data$HospCt, y = data$normalized_deaths, method = "spearman")


pcor.test(x = data$HospCt, y = data$normalized_deaths, 
          z = data$X1.Month.Prior.Inter.Mobility)


Partial Correlation 

library(ppcor)
pcor.test(x = data$HospCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility", "Total_age65plus")], method="spearman")



library(ppcor)
pcor.test(x = data$HospCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility", "NursingCt")], method = "spearman")




library(ppcor)
pcor.test(x = data$NursingCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility")], method = "spearman")


library(ppcor)
pcor.test(x = data$NursingCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013")], method = "spearman")



library(ppcor)
pcor.test(x = data$HospCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013")], method = "spearman")



library(ppcor)
pcor.test(x = data$HospCt, y = data$normalized_deaths, 



library(ppcor)
pcor.test(x = data$HospCt, y = data$normalized_deaths, 
          z = data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility", "Total_age65plus")])



```{r}
pairwise_data = read.csv("../data/processed/local_pairwise_multi_var_unscaled.csv", header = TRUE)
head(pairwise_data)
```

```{r}
library(ppcor)
cor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, method = "spearman")
```


Partial Correlation //*0.06796591, 0.01061533
```{r}
library(ppcor)
pcor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility")], method="spearman")
```

//0.3102586
```{r}
library(ppcor)
pcor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility", "Total_age65plus")], method="spearman")
```

// 1.660636e-05
```{r}
library(ppcor)
pcor.test(x = pairwise_data$Total_age65plus, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility")], method="spearman")
```

**0.1367593, 0.0271566 
```{r}
library(ppcor)
pcor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "Total_age65plus")], method="spearman")
```


// 0.3162988
```{r}
library(ppcor)
pcor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility", "NursingCt")], method="spearman")
```

// 2.514871e-05
```{r}
library(ppcor)
pcor.test(x = pairwise_data$NursingCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility")], method="spearman")
```

**0.2031652, 0.1367593, 0.0271566 
```{r}
library(ppcor)
pcor.test(x = pairwise_data$HospCt, y = pairwise_data$normalized_deaths, 
          z = pairwise_data[, c("Rural.urban_Continuum.Code_2013", "NursingCt")], method="spearman")
```

```{r}
pairwise_PCA_withoutHosp = read.csv("../data/processed/pca_withoutHosp_local_pairwise_multi_var.csv", header = TRUE)
head(pairwise_PCA)
```

// 0.8055295	
```{r}
library(ppcor)
pcor.test(x = pairwise_PCA_withoutHosp$HospCt, y = pairwise_PCA_withoutHosp$normalized_deaths, 
          z = pairwise_PCA_withoutHosp[, c('Principal_Component_1', 'Principal_Component_2', 'Principal_Component_3', 'Principal_Component_4', 'Principal_Component_5', 'Principal_Component_6', 'Principal_Component_7', 'Principal_Component_8', 'Principal_Component_9', 'Principal_Component_10', 'Principal_Component_11', 'Principal_Component_12', 'Principal_Component_13', 'Principal_Component_14', 'Principal_Component_15', 'Principal_Component_16', 'Principal_Component_17', 'Principal_Component_18', 'Principal_Component_19', 'Principal_Component_20', 'Principal_Component_21')], method="spearman")
```
```{r}
library(ppcor)
pcor.test(x = pairwise_PCA_withoutHosp$HospCt, y = pairwise_PCA_withoutHosp$normalized_deaths, 
          z = pairwise_PCA_withoutHosp[, c('Principal_Component_1', 'Principal_Component_2', 'Principal_Component_3')], method="spearman")
```



```{r}
NE_pairwise_data = read.csv("../data/processed/NE_local_pairwise_multi_var_unscaled.csv", header = TRUE)
head(pairwise_data)
```

```{r}
library(ppcor)
cor.test(x = NE_pairwise_data$HospCt, y = NE_pairwise_data$normalized_deaths, method = "spearman")
```


#Partial Correlation 
// 0.1448246 
```{r}
library(ppcor)
pcor.test(x = NE_pairwise_data$HospCt, y = NE_pairwise_data$normalized_deaths, 
          z = NE_pairwise_data[, c("Rural.urban_Continuum.Code_2013", "X2wk.Prior.Intra.Mobility")], method="spearman")
```

```{r}
library(ppcor)
pcor.test(x = NE_pairwise_data$HospCt, y = NE_pairwise_data$normalized_deaths, 
          z = NE_pairwise_data[, c("Rural.urban_Continuum.Code_2013", "Total_age65plus")], method="spearman")
```

```{r}
library(ppcor)
pcor.test(x = NE_pairwise_data$HospCt, y = NE_pairwise_data$normalized_deaths, 
          z = NE_pairwise_data[, c("Rural.urban_Continuum.Code_2013")], method="spearman")
```